Assuming that following odd power identity holds
\begin{align*}
    n^{2m+1} = \sum_{r=0}^{m} \sum_{k=0}^{n-1} \coeffA{m}{r} k^r (n-k)^r
\end{align*}
Our main goal is to identify the set of coefficients $\coeffA{m}{0}, \coeffA{m}{1}, \ldots, \coeffA{m}{m}$
such that identity above is true.

Although, the recurrence relation is already given at~\cite{alekseyev2018mathoverflow}, a few key points in proof
are worth to discuss additionally.

The main idea of Alekseyev's approach was to utilize dynamic programming methods to evaluate the $\coeffA{m}{r}$ recursively,
taking the base case $\coeffA{m}{m}$, then evaluating the next coefficient $\coeffA{m}{m-1}$
by using backtracking, continuing similarly up to $\coeffA{m}{0}$.

Expanding $(n-k)^r$ using Faulhaber's formula yields
\begin{align}
    &\sum_{k=0}^{n-1} k^{j} (n-k)^{j} = \sum_{k=0}^{n-1} \sum_{i} \binom{j}{i} n^{j-i} k^{i+j} \\
    &= \sum_{i} \binom{j}{i} n^{j-i} \frac{(-1)^i}{i+j+1} \left[ \sum_{t} \binom{i+j+1}{t} \bernoulli{t} n^{i+j+1-t} - \bernoulli{i+j+1} \right] \\
    &=\sum_{i,t} \binom{j}{i} \frac{(-1)^i}{i+j+1} \binom{i+j+1}t B_t n^{2j+1-t} - \sum_{i} \binom{j}{i}  \frac{(-1)^i}{i+j+1} B_{i+j+1} n^{j-i}
\end{align}
where $\bernoulli{t}$ are Bernoulli numbers.

\textbf{Comment}: Now let's break down the steps we performed to get formulae above
\begin{itemize}
    \item In (1) we expanded $(n-k)^{j}$ by using Binomial theorem
    \item In (2) we expanded the sum $\sum_{k=0}^{n-1} k^{i+j}$ by using Faulhaber's formula
    $\sum_{k=1}^{n} k^{p} = \frac{1}{p+1}\sum_{t=0}^{p} \binom{p+1}{t} \bernoulli{j} n^{p+1-t}$.
    Note that the Faulhaber's formula above was modified in order to omit summation bounds, meaning that
    \begin{align*}
        \sum_{k=1}^{n} k^{p} = \frac{1}{p+1}\sum_{t=0}^{p} \binom{p+1}{t} \bernoulli{j} n^{p+1-t}
        = \left[ \frac{1}{p+1}\sum_{t} \binom{p+1}{t} \bernoulli{t} n^{p+1-t} \right] - \bernoulli{p+1}
    \end{align*}
    \item In (3) we expand brackets by merging two sums
\end{itemize}
Now, we notice that
\begin{align}
    \sum_{i} \binom{j}{i} \frac{(-1)^i}{i+j+1} \binom{i+j+1}t
    =\begin{cases}
         \frac{1}{(2j+1)\binom{2j}j}, & \text{if } t=0;\\
         \frac{(-1)^j}{t}\binom{j}{2j-t+1}, & \text{if } t>0.
    \end{cases}
\end{align}
\textbf{Comment}: The source or proof of identity (4) is not clear yet.
It would be nice to provide it.

Hence, introducing $\ell=2j+1-t$ and $\ell = j-i$ respectively, we get
\begin{align}
    \sum_{k=0}^{n-1} (n-k)^j k^j
    &= \frac{1}{(2j+1)\binom{2j}j} n^{2j+1} + \sum_{\ell} \frac{(-1)^j}{2j+1-\ell}\binom{j}{\ell}B_{2j+1-\ell}n^{\ell}
    - \sum_{\ell} \binom{j}{\ell} \frac{(-1)^{j-\ell}}{2j+1-\ell} B_{2j+1-\ell}n^{\ell} \\
    &=\frac{1}{(2j+1)\binom{2j}j} n^{2j+1} + 2\sum_{\text{odd }\ell} \frac{(-1)^j}{2j+1-\ell}\binom{j}{\ell}B_{2j+1-\ell}n^{\ell}
\end{align}
\textbf{Comment}: Let's break down what is going in (5) and (6)
\begin{itemize}
    \item \textit{Step 5.1}: Double sum $\sum_{i,t}$ simplified to single one $\sum_t$ by means of (4).
    \item \textit{Step 5.2}: The term $\frac{1}{(2j+1)\binom{2j}j} n^{2j+1}$ moved out of summation by means of (4).
    It is iteration step $t=0$.
    \item \textit{Step 5.3}: Introducing $\ell=2j+1-t$ and $\ell = j-i$ to sums $\sum_t$ and $\sum_i$ to collapse common terms in (5).
    \item \textit{Step 5.4}: Expression with common terms collapsed (6).
\end{itemize}
Using the definition of $\coeffA{m}{j}$, we obtain the following identity for polynomials in $n$
\begin{align}
    \sum_{j} \coeffA{m}{j} \frac{1}{(2j+1)\binom{2j}j}n^{2j+1}
    + 2 \sum_{j,\text{ odd }\ell} \coeffA{m}{j} \binom{j}{\ell} \frac{(-1)^j}{2j+1-\ell} B_{2j+1-\ell}n^{\ell} \equiv n^{2m+1}
\end{align}
Taking the coefficient of $n^{2m+1}$ we get
\begin{align}
    \coeffA{m}{m} = (2m+1)\binom{2m}{m}
\end{align}
\textbf{Comment}: It is not clear how exactly $\coeffA{m}{m} = (2m+1)\binom{2m}{m}$ follows.
As I understand, here is about \textit{Taking coefficient of} in context of generating functions?
Meaning that coefficient of $2m+1$ so that $j=m$ in $\sum_{j} \coeffA{m}{j} \frac{1}{(2j+1)\binom{2j}j}n^{2j+1}$?
Hence, coefficient of it to be $\coeffA{m}{m} \frac{1}{(2m+1)\binom{2m}{m}}$.
To evaluate $\coeffA{m}{m} = (2m+1)\binom{2m}{m}$ it should be assumed that $\coeffA{m}{m} \frac{1}{(2m+1)\binom{2m}{m}} = 1$,
which is indeed true because of $n^{2m+1}$ in RHS.
